Architectures for workflow integration in science gateways

### 2016-04-13 paper.tex
Updates on Figures
Updates in paper.tex
Added figure on graphical notations

\usepackage[x11names,dvipsnames,table]{xcolor} %for use in color links
\usepackage{svg}
\usepackage{url}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}

\newcommand{\todo}[1]{\color{blue}\xspace\emph{#1}\xspace\color{black}}
\newcommand{\note}[1]{\color{blue}\textbf{Note: }\textit{#1} \color{black}}

@@

%\authors{Tristan Glatard, Marc-Etienne Rousseau, Pierre Rioux, Samir
%Das, Natacha Beck, Reza Adalat, Pierre Bellec, Pierre-Olivier Quirion,
%S\'ilvia D. Olabarriaga, Sorina Camarasu-Pop, Alan C. Evans}
% Rafael? Ewa? Peter Kacsuk? Johan? Satra? Najma?

@@

Architectures are defined below from their main components and the
interactions between these components.

\todo{Introduce the notion of architectural diagram with an abstract
  figure. Mention arrows, boxes, box with dotted lines, red color,
  tasks, data.}

@@

@@

@@

\begin{figure}
\centering
\def\svgwidth{0.5\columnwidth}
\input{figures/tight.pdf_tex}
\caption{Tight integration}
\label{archi:tight}
\end{figure}

@@

This architecture is largely adopted, in systems such as Apache
Airvata~\cite{marru2011apache}, Vine
Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual
Imaging Platform~\cite{GLAT-13}, the WS-PGRADE/gUSE
framework~\cite{Kacsuk2012} and the numerous science gateway instances
that use it~\cite{kacsuk2014science}.
\begin{figure}
\centering
\def\svgwidth{0.5\columnwidth}
\input{figures/service.pdf_tex}
\caption{Service integration}
\label{archi:service}
\end{figure}

@@

This model is implemented in CBRAIN~\cite{SHER-14} where it is used to
integrate the PSOM workflow engine and the FSL toolkit through its
\texttt{fsl\_sub} tool. In particular, the CBRAIN-PSOM integration is
described in~\cite{GLAT-16} and uses an agent computing model (a.k.a pilot
jobs).
\begin{figure}
\centering
\def\svgwidth{0.5\columnwidth}
\input{figures/sub-task.pdf_tex}
\caption{Sub-tasking}
\label{archi:sub-task}
\end{figure}

\subsection{Pool model}
\label{sec:pool}
See Figure~\ref{archi:agent}. Workflows are submitted by the science
gateway to a pool to which agents connect asynchronously to retrieve
and execute workflows (interaction \texttt{f}). Agents may be started according to various
policies, for instance to ensure load balancing. Agents may wrap
different types of workflow engines. This model was implemented in the
SHIWA pool~\cite{ROGE-13}.
\begin{figure}
\centering
\def\svgwidth{0.8\columnwidth}
\input{figures/agent.pdf_tex}
\caption{Pool model}
\label{archi:agent}
\end{figure}

@@

\begin{figure}
\centering
\def\svgwidth{0.48\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.48\columnwidth}
\input{figures/nested-2.pdf_tex}
\caption{Nested workflows. Left: abstract model. Right: instantiation with service invocation.}
\label{archi:nested}
\end{figure}

@@

\begin{figure}
\centering
\def\svgwidth{0.48\columnwidth}
\input{figures/import-1.pdf_tex}
\def\svgwidth{0.48\columnwidth}
\input{figures/import-2.pdf_tex}
\caption{Workflow import. Left: abstract model. Right: instantiation with service invocation.}
\label{archi:import}
\end{figure}

>>>>

\usepackage[x11names,dvipsnames,table]{xcolor} %for use in color links
\usepackage{subfig}
\usepackage{svg}
\usepackage{url}

\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}

\newcommand{\todo}[1]{\color{blue}\xspace[\emph{#1}]\xspace\color{black}}
\newcommand{\note}[1]{\color{green}\textbf{Note: }\textit{#1} \color{black}}

@@

@@

Figure~\ref{fig:notations} shows the graphical notations used to
describe the architectures in the reminder of this
Section. Architectures are described from their main software
components and interactions.

@@

\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{figures/notations.pdf_tex}
\caption{Graphical notations}
\label{fig:notations}
\end{figure}

@@

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Sub-tasking]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow import. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}

@@

@@

This architecture is largely adopted, in systems such as Apache
Airvata~\cite{marru2011apache}, Vine
Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual
Imaging Platform~\cite{GLAT-13}, the WS-PGRADE/gUSE
framework~\cite{Kacsuk2012} and the numerous science gateway instances
that use it~\cite{kacsuk2014science}.

@@

This model is implemented in CBRAIN~\cite{SHER-14} where it is used to
integrate the PSOM workflow engine and the FSL toolkit through its
\texttt{fsl\_sub} tool. In particular, the CBRAIN-PSOM integration is
described in~\cite{GLAT-16} and uses an agent computing model (a.k.a pilot
jobs).

\subsection{Pool model}
\label{sec:pool}
See Figure~\ref{archi:agent}. Workflows are submitted by the science
gateway to a pool to which agents connect asynchronously to retrieve
and execute workflows (interaction \texttt{f}). Agents may be started according to various
policies, for instance to ensure load balancing. Agents may wrap
different types of workflow engines. This model was implemented in the
SHIWA pool~\cite{ROGE-13}.

@@

@@

\todo{workflow import is an offline process.}
